\
#include $<\tilde{ }$/graph/graph/Vertex.h$>$

\
class Vertex: public TaggedObject

\
TaggedObject

\
\
Vertex is the abstraction of a vertex in a graph. It has a color, weight
and a temporary integer value associated with it. Also associated with
it is an integer reference, which can be used to identify an object of
some type the vertex is representing and in integer temporary variable
for algorithms which work with graphs.\
\
// Constructor

\
\
// Destructor

*virtual $\tilde{}$Vertex();*\
// Public Methods

*virtual void setWeight(double newWeight);*

*virtual void setColor(int newColor);*

*virtual void setTmp(int newTmp);*

*virtual int getTag(void) const;*.

*virtual int getRef(void) const;*

*virtual double getWeight(void) const;*

*virtual int getColor(void) const;*

*virtual int getTmp(void) const;*

*virtual int addEdge(int otherTag);*

*virtual int getDegree(void) const;*

*virtual const ID &getAdjacency(void) const;*

\
*virtual void Print(OPS_Stream &s, int flag =0);*

\
*Vertex(int tag, int ref, double weight=0, int color =0);*

To construct a Vertex whose tag, reference, weight and color are as
given by the arguments. The degree of the vertex is set to $0$. The
integer *tag* is passed to the TaggedObject classes constructor.\
\
*virtual $\tilde{}$Vertex();*

Does nothing.\
\
*virtual void setWeight(double newWeight);*

To set the weight of the vertex to *newWeight*\
*virtual void setColor(int newColor);*\
To set the color of the vertex to *newColor*\
*virtual void setTmp(int newTmp);*\
To set the temporary variable of the vertex to *newTmp*\
*virtual int getTag(void) const;*.\
Returns the vertices tag.\
*virtual int getRef(void) const;* \
Returns the vertices integer reference.\
*virtual double getWeight(void) const;*\
Returns the vertices weight.\
*virtual int getColor(void) const;* \
Returns the vertices color.\
*virtual int getTmp(void) const;* \
Returns the vertices temporary variable.\
*virtual int addEdge(int otherTag);* \
If the adjacency list for that vertex does not already contain
*otherTag*, *otherTag* is added to the adjacency list and the degree of
the vertex is incremented by $1$. Returns a $0$ if sucessfull, a $1$ if
edge already existed and a negative number if not. Note that no check is
done by the vertex to see that a vertex with *otherTag* exists in the
graph. The adjacency list for a Vertex is stored in an ID object
containing the adjacent Vertices tags. A check is made to see if
*otherTag* is in this ID using *getLocation()*, if it needs to be added
the *\[degree\]* operator is invoked on the ID.\
*virtual int getDegree(void) const;*\
Returns the vertices degree.\
*virtual const ID &getAdjacency(void) const;*\
Returns the vertices adjacency list, this is returned as an ID whose
components are tags for vertices which have been successfully added.\
*virtual void Print(OPS_Stream &s, int flag=0);*\
Prints the vertex. If the *flag = 0* only the vertex tag and adjacency
list is printed. If the *flag =1* the vertex tag, weight and adjacency
are printed. If the *flag =2* the vertex tag, color and adjacency are
printed. If the *flag =3* the vertex tag, weight, color and adjacency
are printed.\
